Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2): Submission, Peer-Review, and Sorting Process, and Results

### 2014-11-12 WSSSPE2_preworkshop_report/WSSSPE2_review_report.tex
fixing David's affil and the typos he caught

\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(affil?)}$, \\
Matthew Turk$^{(2)}$, Colin C. Venters$^{(6)}$, Nancy Wilkins-Diehr$^{(7)}$}

@@

\thanks{{}$^{(6)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}

\thanks{{}$^{(7)}$ University of California-San Diego, San Diego, CA, USA}

\begin{abstract}
This technical report discusses the submission and peer-review process used by the Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2) and the results of that process.  It is intended to record both the alternative submission and program organization model used by WSSSPE2 as well as the papers associated with the workshop that resulted from that process.
\end{abstract}

@@

\todo{fix David's affil}

@@

WSSSPE2 will include two keynote presentations, and lightening talks from accepted paper authors, in addition to a set of breakout sessions.  The breakouts will allow attendees to participate in discussions about sustainability, future actions, and two of the five areas that resulted from the community submission, review, and grouping process.  There will also be reporting from the breakout groups to collect information for all attendees, as well as people who were not able to attend, to understand the discussions.

>>>>

\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$}

@@

\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}

\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}

\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}

\begin{abstract}
This technical report discusses the submission and peer-review process used by the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2) and the results of that process.  It is intended to record both the alternative submission and program organization model used by WSSSPE2 as well as the papers associated with the workshop that resulted from that process.
\end{abstract}

@@

@@

WSSSPE2 will include two keynote presentations, and lightning talks from accepted paper authors, in addition to a set of breakout sessions.  The breakouts will allow attendees to participate in discussions about sustainability, future actions, and two of the five areas that resulted from the community submission, review, and grouping process.  There will also be reporting from the breakout groups to collect information for all attendees, as well as people who were not able to attend, to understand the discussions.
